---
title: "Clean Nunn-Wantchekon AER 2011 Data"
author: "Jeffrey Arnold"
date: "4/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Download the replication data for

> Nunn, Nathan, and Leonard Wantchekon. 2011. "The Slave Trade and the Origins of Mistrust in Africa." American Economic Review, 101 (7): 3221-52. DOI:10.1257/aer.101.7.3221

Clean the data and save to R objects in `data/`.

In addition to the original individual-level data, this will also create a ethnic group level dataset, as was used in one of the replications.

# Prerequisites 

```{r message=FALSE}
library("tidyverse")
library("haven")
library("recipes")
library("httr")
```

```{r}
DATA_DIR <- here::here("data")
dir.create(DATA_DIR, showWarnings = FALSE)
```

# Download

Download replication zip file if it does not exist.

```{r}
URL <- "https://www.aeaweb.org/aer/data/dec2011/20090252_data.zip"
DOWNLOAD_DIR <- here::here("downloads")
zip_file <- file.path(DOWNLOAD_DIR, basename(URL))
  
dir.create(file.path(DOWNLOAD_DIR), showWarnings = FALSE)
if (!file.exists(zip_file)) {
  GET(URL, write_disk(zip_file))  
}
```

# Individual Level Data

Clean the dataset largely to account for differences in how R and Stata model data.

```{r}
dta_file <- "NUNN_WANTCHEKON_AER_2011_REPLICATION_FILES/Nunn_Wantchekon_AER_2011.dta"
nw2011 <- read_dta(unz(zip_file, dta_file)) %>%
  mutate_if(is.labelled, haven::as_factor) %>%
  mutate_at(vars(religion, education, occupation, living_conditions,
                 v30), funs(as.factor)) %>%
  mutate(v33 = as.numeric(v33))
```

```{r}
save(nw2011, file = file.path(DATA_DIR, "nw2011.rda"),
     compress = "bzip2")
```


# Ethnicity-Level data

The main treatment variable (extent of slavery) is defined at the ethnicity level.
Create an ethnicity-level dataset, with averages of the other variables.
This was one of the robustness checks in the Nunn-Wantchekon paper.

```{r}
nw2011_ethnicities <- 
  recipe(~ ., data = nw2011)  %>%
  step_dummy(isocode) %>%
  step_dummy(religion) %>%
  step_dummy(education) %>%
  step_dummy(occupation) %>%
  step_dummy(living_conditions) %>%
  step_dummy(v30) %>%
  prep(train = nw2011, retain = TRUE) %>%
  juice()

nw2011_ethnicities <- nw2011 %>%
  filter(murdock_name != "") %>%
  group_by(murdock_name) %>%
  summarise_at(vars(age, male, urban_dum, 
                    matches("^occupation_"),                    
                    matches("^living_condition_"),
                    matches("^education_"),
                    matches("^religion_"),
                    # other controls
                    ln_init_pop_density,
                    malaria_ecology,
                    total_missions_area,
                    explorer_contact,
                    railway_contact,
                    cities_1400_dum,
                    matches("^v30_"),
                    v33,
                    # treatment
                    exports, export_area, export_pop, ln_export_area,
ln_export_pop,
                    trust_neighbors, trust_relatives, trust_local_council,
                    # covariate
                    intra_group_trust, inter_group_trust,
                    district_ethnic_frac, frac_ethnicity_in_district
                    ),
               funs(mean(., na.rm = TRUE)))

```

```{r}
save(nw2011_ethnicities, file = file.path(DATA_DIR, "nw2011_ethnicities.rda"),
     compress = "bzip2")
```

# Original Programming Environment

```{r}
sessionInfo()
```
