---
title: "Replication of Nunn and Wantchekon (2011) 'The Slave Trade and the Origins of Mistrust in Africa'"
author: "Jeffrey B. Arnold"
output: html_document
editor_options: 
  chunk_output_type: console
---

## Introduction

This will replicate Nunn and Wantchekon (2011) "[The Slave Trade and the Origins of Mistrust in Africa](https://www.aeaweb.org/articles?id=10.1257/aer.101.7.3221)" using Bayesian statistical methods.

The abstract for this paper is

> We show that current differences in trust levels within Africa can be
> traced back to the transatlantic and Indian Ocean slave trades.
> Combining contemporary individual-level survey data with historical data
> on slave shipments by ethnic group, we find that individuals whose
> ancestors were heavily raided during the slave trade are less trusting
> today. Evidence from a variety of identification strategies suggests
> that the relationship is causal. Examining causal mechanisms, we show
> that most of the impact of the slave trade is through factors that are
> internal to the individual, such as cultural norms, beliefs, and values.

You can also read the author's summary [here](https://voxeu.org/article/understanding-long-run-effects-africa-s-slave-trades).

## Prerequisites

```{r}
library("tidyverse")
library("rstan")
```


## Data

Replication data for this paper is available on the *American Economic Review* page for the [article](https://www.aeaweb.org/aer/data/dec2011/20090252_data.zip).
This project contains cleaned versions or the original data, created by the `clean.Rmd` file.

There are two datasets 

-   `data/nw2011.rda`: Individual level data
-   `data/nw2011_ethnicities`: Ethnic group level averages

Load the data
```{r}
(data("nw2011"))
```
```{r}
(data("nw2011_ethnicities"))
```
Note: this works because `data()` looks for datasets in `./data` before looking in packages.

## Model

### Normal-No Covariates

What's in the data?
```{r results='hide'}
glimpse(nw2011_ethnicities)
```

```{r}
ggplot(nw2011_ethnicities, aes(x = trust_neighbors)) +
  geom_density() + 
  geom_rug()
```

# No-Covariate Models

```{r}
data <- list(y = na.omit(nw2011_ethnicities$trust_neighbors))
data$n <- length(data$y)
```
```{r}
mod1 <- stan("stan/mean.stan", data = data)
```




## References

-   Nunn, Nathan, and Leonard Wantchekon. 2011. "[The Slave Trade and the Origins of Mistrust in Africa](https://dx.doi.org/10.1257/aer.101.7.3221)" *American Economic Review*, 101 (7): 3221-52.
-   Nathan Nunn (2017) [Understanding the long-run effects of Africa’s slave trades](https://voxeu.org/article/understanding-long-run-effects-africa-s-slave-trades) Vox.eu
